\thispagestyle{empty}

%TC:ignore

\section*{\centering Abstract}

Discord \cite{discord} is a video and text platform that allows users to set up servers for small communities. The Department of Computer Science has used it to create virtual module servers, similar to the current blackboard alternatives. The main issue however with these servers, however, is that they are always public so when an invite link is distributed it can be sent to anyone including people who are not related in any way to the University. This opens up servers to potential attacks and misuse. AberLink aims to solve this problem by providing the department with a mechanism to control access to module servers based on their membership with the University. This service also provides attendance monitoring of practicals which are located online on Discord in a specific server and at a specific time. This data is then fed into the central attendance monitoring system `Student Record'.

AberLink consists of 2 components; a website that allows users to link up Discord \cite{discord} accounts to University accounts and a Discord bot called AberLink that controls users' access to module servers and records students' attendance. 

The service was developed on the Linux distribution Debian 10 (Buster) \cite{debian} and uses the open-source HTTP server Apache2.0 \cite{apache2} for website hosting along with the Python framework Django \cite{Django} for the website. This website is locked behind the Open-ID Connect \cite{OpenID} login system that only authenticates users with Aber accounts. Once logged in a user can link multiple Discord accounts to their Aber account. The service also employs the use of a Discord bot using the Python framework Discord.py \cite{discord.py}. The back-end database uses PostgreSQL \cite{psql} and is used to communicate between the website and the Discord bot. 

The AberLink Discord bot is based on two previous bots called Aber Verify Bot \cite{aber_verify} and I am here! \cite{i_am_here}, both created my Neal Snooke. These bots verified students' Discord accounts and helped to mark attendance during practicals respectively. AberLink greatly modifies the original implementation of these bots to use a proper back-end database and an API to update attendance.

%TC:endignore