\chapter{README aberlink-for-staff}{%
\section{AberLink for staff}\label{aberlink-for-staff}}

For my major project, I have created a Discord bot and Website that will
be replacing the Discord bots Aber Verify and I am here next year. As
this project will be deployed to module servers and eventually this
server I would appreciate it if you could come over to my server and
test out any of the bot's features. If you can find any way to break the
bot or identify any edge cases that I have missed that would be great.

Please note that by logging into this website you agree to the
Participation Agreement form found here:
\url{https://mmp-joa38.dcs.aber.ac.uk/privacy-policy}

\hypertarget{getting-authenticated-with-aberlink}{%
\subsection{Getting authenticated with
AberLink}\label{getting-authenticated-with-aberlink}}

Go to the website \url{https://mmp-joa38.dcs.aber.ac.uk/} (VPN required)
and log in with your Aber credentials. This should save your information
to the database and you should be greeted with a nice welcome page
greeting you with a button on the screen to link a Discord account.

Click the button to link a Discord account to your Aber account and log
in with your Discord credentials. This should now save your Discord UUID
to the database and link it to your Aber account. You should now be
redirected back to the homepage where you can view your linked Discord
account. You can also link up multiple Discord accounts to the same Aber
account so feel free to try that feature out.

There are also some other pages available in the navigation bar for you
to use and mess around with. Please feel free to make comments on these
pages and let me know.

In the top right of the navigation bar click on the Admin site to view
all the information on the authenticated Aber accounts and their linked
Discord accounts. Feel free to mess about in this panel but avoid
deleting users that aren't yourself.

\hypertarget{add-the-bot-to-your-server}{%
\subsection{Add the bot to your
server}\label{add-the-bot-to-your-server}}

If you want to try the Discord bot please use this invite link here and
add it to your server (Caution as this is still in beta). WARNING:
adding this bot to a current module server is not advised as it may not
work fully as intended.
\url{https://discord.com/api/oauth2/authorize?client_id=807609453972422676\&permissions=8\&redirect_uri=https\%3A\%2F\%2Fmmp-joa38.dcs.aber.ac.uk\%2Foauth2\%2Flogin\%2Fredirect\&scope=bot}

After the bot has been added to the server follow the onscreen commands
and use it as you would demobot. It uses the same principles so should
be relatively straight forward.

\hypertarget{join-the-test-server-alternative}{%
\subsection{Join the test server
(alternative)}\label{join-the-test-server-alternative}}

Join the Discord server \url{https://discord.gg/XKtfya9NHF}

If you'd prefer not to mess around with the bot in your server feel free
to join the current test server for the bot and try out its features
there instead.

I'd really appreciate it if you could leave some feedback for me; either
through the Discord server by rating your experience and leaving a note
in the \texttt{\#feedback} channel or by email to joa38@aber.ac.uk

Every little piece of feedback can help to make the project better and
improve my project report.

Thank you so much for testing this project for me,

Joel