\chapter{Testing}

%Detailed descriptions of every test case are definitely not what is required here. What is important is to show that you adopted a sensible strategy that was, in principle, capable of testing the system adequately even if you did not have the time to test the system fully.

%Provide information in the body of your report and the appendix to explain the testing that has been performed. How does this testing address the requirements and design for the project?

%How comprehensive is the testing within the constraints of the project?  Are you testing the normal working behaviour? Are you testing the exceptional behaviour, e.g. error conditions? Are you testing security issues if they are relevant for your project? 

%Have you tested your system on ``real users''? For example, if your system is supposed to solve a problem for a business, then it would be appropriate to present your approach to involve the users in the testing process and to record the results that you obtained. Depending on the level of detail, it is likely that you would put any detailed results in an appendix.

%Whilst testing with ``real users'' can be useful, don't see it as a way to shortcut detailed testing of your own. Think about issues discussed in the lectures about until testing, integration testing, etc. User testing without sensible testing of your own is not a useful activity.

%The following sections indicate some areas you might include. Other sections may be more appropriate to your project.   

As previously mentioned in section \ref{sec1:pro} a Feature Driven Development (FDD) approach was used for this project, working in one week iteration windows to build and test the software. This included all of the testing sections mentioned below apart from automated testing which was completed at the end of the project instead.

The Discord.py Python framework does not contain any unit testing and there are no third party libraries which sufficiently perform this job. For the Django framework however there are some unit tests built in so they have been used in this project and are detailed further on in section \ref{sec4:unit-web}. These Django tests are used to cover both the website and the database as the website cannot be tested by itself. 

\section{Sample Data}
Sample data was considered for this project however it would be very difficult to implement because the OpenID Connect \cite{OpenID} system used to authenticate and log users in relies on a proper database to pull user data from. The University was not comfortable with creating and supplying fake user accounts that would authenticate with this system as the database where these would be used is currently live. This would mean that they could be stolen and used to access live systems such as Student Record or blackboard. The alternative to this would mean that a mock database would be needed which would take up a considerable work to create. The workaround for this system is far simpler and involved asking both staff and students to try out the system and test it until it breaks. The outcomes of this are detailed in section \ref{sec4:user-tesing}.

\section{Automated Testing}
Automated testing has been difficult for this project as mentioned above. Originally there was a plan to include automated testing by using the DevOps frameworks in Git, however as the universities GitLab instance was used then there was no access to dedicated pipelines/kubernite clusters to build and run the code.  

\subsection{Unit Tests}

\subsubsection{Website \& Database}\label{sec4:unit-web}
Django provides some useful documentation (\href{https://docs.djangoproject.com/en/3.1/topics/testing/}{https://docs.djangoproject.com/en/3.1/topics/testing/}) for creating unit tests for both Django and the database/user models. These tests are useful for checking that Discord accounts and OpenID Connect \cite{OpenID} Aber accounts link up properly and that webpage urls are correct and render the appropriate content. All of the following tests can be found in the file located in this path \verb|src\AberLinkAuthentication\login\tests.py|. 

Below are two testing classes; one called TestUrls and one called TestModels. These are responsible for testing that the urls are correctly found and that adding new users to the database works as intended. Included below is an example of each test:

\begin{figure}[H]
\begin{lstlisting}[language=Python]
def test_url_discord_redirect(self):
    url = reverse('Discord-response')
    self.assertEquals(resolve(url).func, views.discord_oauth2_redirect)
\end{lstlisting}
\caption{Django URL render test}
\label{fig:django-url}
\end{figure}
As seen above the test function simply gets the name of the url `Discord-response' and then checks that it returns the correct Python function (view) to render that page

\begin{figure}[H]
\begin{lstlisting}[language=Python]
def test_model_openidc_user_staff(self):
    self.openidc_user2 = OpenIDCUser.objects.create(
        username="abc123",
        name="Bob Ross",
        email="abc123@aber.ac.uk",
        usertype="staff"
    )
    self.assertEquals(self.openidc_user2.username, "abc123")
    self.assertEquals(self.openidc_user2.name, "Bob Ross")
    self.assertEquals(self.openidc_user2.email, 
    "abc123@aber.ac.uk")
    self.assertEquals(self.openidc_user2.usertype, "staff")
    self.assertEquals(self.openidc_user2.is_admin, True)
\end{lstlisting}
\caption{Django database render test}
\label{fig:django-database}
\end{figure}
This function creates a new user object and then checks to make sure that the user has been given the admin and has the usertype of staff.

\subsubsection{Discord}
Unit testing in Discord.py is impossible as there is no included framework for it and there are no external libraries capable of testing to check that it works. Please see section \ref{sec4:user-tesing} for more info on testing.

\subsection{Stress Testing}
To test the websites capacity to deal with 100s of requests ApacheBenchmark \cite{apacheBenchmark} is used which is a built into the Apache2 \cite{apache2} and is a module used to request a webpage and measure response time. To test this the OpenID Connect \cite{OpenID} authentication system  was temporarily disabled so that HTML gets served to the incoming requests instead of being redirected to the login page. Due to the nature of the websites implementation you cannot query the main page because the user is not authenticated and the page cannot display information on the user, however it can query one of the subpages that does not require authentication. The following line of code was used to complete the request with 1000 requests and 100 concurrent threads to attempt to tank the website's performance.

\verb|ab -n 1000 -c 100 https://mmp-joa38.dcs.aber.ac.uk/privacy-policy|

This command generates the following report which shows that the website is capable at easily handling this many requests simultaneously. The longest response time for serving the requests was 642ms which is still adequately fast for the average user and shows that Django handles requests reasonable well. It can also serve on average 174 requests per second and I expect that the website will never be receiving more that 300 requests at the exact same time which can definitely be handled as seen from these results. Another factor to consider is that this development build is currently running on a small container that only has access to a small amount of resources whereas in the final build it will have access to far more resources so could serve requests up even quicker.

%\begin{figure}[hbt!]
\begin{verbatim}
Server Software:        Apache/2.4.38
Server Hostname:        mmp-joa38.dcs.aber.ac.uk
Server Port:            443
SSL/TLS Protocol:       TLSv1.2,ECDHE-RSA-AES256-GCM-SHA384,2048,256
Server Temp Key:        X25519 253 bits
TLS Server Name:        mmp-joa38.dcs.aber.ac.uk

Document Path:          /privacy-policy
Document Length:        12448 bytes

Concurrency Level:      100
Time taken for tests:   5.719 seconds
Complete requests:      1000
Failed requests:        0
Total transferred:      12734000 bytes
HTML transferred:       12448000 bytes
Requests per second:    174.86 [#/sec] (mean)
Time per request:       571.882 [ms] (mean)
Time per request:       5.719 [ms] (mean, across all concurrent requests)
Transfer rate:          2174.50 [Kbytes/sec] received

Connection Times (ms)
              min  mean[+/-sd] median   max
Connect:        9  422 105.1    458     547
Processing:     7   86  61.1     67     404
Waiting:        6   83  60.1     64     381
Total:         42  508  96.3    531     642

Percentage of the requests served within a certain time (ms)
  50%    531
  66%    550
  75%    560
  80%    565
  90%    574
  95%    583
  98%    593
  99%    602
 100%    642 (longest request)
\end{verbatim}
%\caption{Output from running Apache Benchmark on the website}
%\label{fig:ab}
%\end{figure}

\section{User Interface Testing}
Testing the user interface for the AberLink is mostly straight forward as Discord has full control over the UI so I have had no testing to do on that front.

The UI of the website uses the library Bootstrap \cite{bootstrap} as it is built from the ground up with responsive design in mind and saves a lot of time that would be required to re-learn CSS fully. This meant that website would scale very nicely and uniformly depending on screen size. To ensure that the website scales and performs well the website and all of its content have been tested on multiple devices. It has been tested on mobile devices, iPads and laptops with screens ranging from 11in to 40in using Safari, Chrome, Edge and Firefox. The website has also been tested on HTML the validation website \href{https://validator.w3.org/}{https://validator.w3.org/} to ensure that there are no large errors that may cause the website to not load on certain machines.

\section{User Testing}\label{sec4:user-tesing}
Due to the nature of Feature Driven Development every time a new feature was implemented it would be tested to ensure that it passed the bare minimum of requirements. I used the testing table located in Appendix D as a guide while working on this project. This gave me the mindset that you develop small sections of code and then review what effect they have on the system. This helps to catch errors and it is much easier to backtrack through small changes made to code.

At the end of this project during the final week some user testing was conducted. Through my project supervisor I reached out to the lecturers (document that can be found in Appendix E) so that they could test the AberLink service and Discord bot to see if it was intuitive and met their standards. This also helped as I had other staff that could test the administration panels of the website and inform me if there were any additional features that could be added to the project.

Through the Comp Sci Community Hub Discord server I asked users if they could try out the login system on the website and Discord bot to see how intuitive they were to use. Feedback from students was extremely helpful as some of them attempted to break the bot and test edge cases that I had previously not thought of. 

Early on there were many requests to fix certain issues or add new features so I used GitLab issues to track these request. I have included the list of issues and requests that testers made to improve their experience of the service below. All of the following issues have been addressed and fixed to improve the service's experience.

\begin{itemize}
    \item Privacy policy is lackluster and needs more detail - \textit{Michael West \& Ben Ackerley}
    \item Make the webpage \href{https://mmp-joa38.dcs.aber.ac.uk/privacy-policy}{\nolinkurl{https://mmp-joa38.dcs.aber.ac.uk/privacy-policy}} readable without signing in so that users can read privacy policy before hand - \textit{Michael Antony West \& Ben Ackerley}
    \item Remove case sensitivity for Discord commands - \textit{Michael West}
    \item Add VPN information to message that contain link to website - \textit{Joel Adams}
    \item Automatically setting nicknames when the bot joins a new server was not working - \textit{Michael West}
    \item Add a small alert to the website when a user registers their account stating that it is now linked for use in Aberystwyth module servers - \textit{Joseph Metcalfe}
    \item Add command to tell the user to configure the bot on join to a new server - \textit{Michael West \& Sivert Hellvik Havso}
    \item User cannot be sent a direct messages on Discord because they have feature disabled - \textit{Nathan Williams \& Ben Ackerley}
    \item Better error messages when commands do not work so that they are more informative - \textit{Neal Snooke \& Joel Adams}
    \item Added feature to allow user that requests command getOpenID to delete output from command - \textit{Chris Loftus}
\end{itemize}

Users were also asked to provide a rating on their experience using AberLink. Below is a table of the gathered user data.

\begin{table}[H]
    \centering
    \begin{tabular}{|p{2cm}|p{2cm}|p{10cm}|}
        \hline
        Name & Satisfied? & Comments \\
        \hline
        Joseph Metcalfe & \color{ForestGreen}Yes & \textit{I found as a student user that this system is much more user friendly than previous verification bots and reduces any potential user confusion to a good degree, which had previously been a problem. The system had no unexpected steps or bloat that I wasn't expecting and does its job well and reliably.  This system also appears to be easier for module coordinators to use compared to previous bots with more guidance given by the bot itself on setting up a server with it which should be helpful for some modules} \\
        \hline
        Michael West & \textcolor{red}{No} (after changes \textcolor{ForestGreen}{Yes}) & \textit{I didn't like how I was send into a channel that I didn't have permissions to access upon joining this server, it was rather disorienting. When I added AberLink to a new server and ran the build command, it told me I didn't have the correct role. It would be helpful if the bot could either create the role and add me to it or tell me I need to make the role myself.} \\
        \hline
        Sivert Hellvik Havso & \color{ForestGreen}Yes & \textit{I will second what Michael said earlier that it would be nice if it straight away told you that you have to give yourself a certain role and run the !build command. Other than that I found the bot to be intuitive to use both as a user and when adding it to my own server.} \\
        \hline
        Sam Lewis & \color{ForestGreen}Yes & \textit{it doesn't dispense a cheese and onion pasty out of the monitor for when I link my aber account... I rate 0/10 points... please fix as soon as possible} \\
        \hline
        Nathan Williams & \color{ForestGreen}Yes & \textit{N/A} \\
        \hline
        Phil Mottershead & \color{ForestGreen}Yes & \textit{N/A} \\
        \hline
        Jenny Thyer & \color{ForestGreen}Yes & \textit{10/10 the system is easy to set up for someone with little experience of managing discord servers. 3/10 the seagull logo should be fatter and angry to better represent the average seagull in Aber} \\
        \hline
        Ben Ackerley & \color{ForestGreen}Yes & \textit{N/A} \\
        \hline
        Alex Baldwin & \color{ForestGreen}Yes & \textit{Couldn't even use it because I didn't have the VPN - Highly recommended} \\
        \hline
        Chris Loftus & \color{ForestGreen}Yes & \textit{N/A} \\
        \hline
        Jack Tugby & \color{ForestGreen}Yes & \textit{N/A} \\
        \hline
        Amanda Clare & \color{ForestGreen}Yes & \textit{N/A} \\
        \hline
    \end{tabular}
    \caption{Table displaying users feedback on using AberLink}
    \label{tab:service-response}
\end{table}

The comments received from these users show that the system is straight forward and easy to use. Wherever users had issues to raise they were addressed and fixed before final deployment. The feedback supplied by Alex Baldwin is very interesting as it highlights where the limits of this service are as he could not actively test the system. This does help to indicate to the department that this service should be available without access to the VPN as many students are still studying remotely.

\subsection{Attendance API Endpoint Testing}
The supplied API for attendance has been tested using user testing and the University provided me with 3 different endpoints to test. They are listed below along their responses.

\begin{verbatim}
https://integration.aber.ac.uk/joa38/good.php
{"status_updated":"true","request":"200","module_code":"CS32120"}    
\end{verbatim}

\begin{verbatim}
https://integration.aber.ac.uk/joa38/bad.php
{"status_updated":"false","request":"400",
"error_message":"Unknown user or no event"}
\end{verbatim}

\begin{verbatim}
https://integration.aber.ac.uk/joa38/submit.php
Actual live endpoint. Returns either of the two JSON messages 
above along with the corrected module_code
\end{verbatim}

\section{Functional Requirements}\label{sec4:fr}
The final testing was conducted using a list of functional requirements set out in section \ref{sec1:fr} and the testing table can be found in Appendix \ref{tab:fr-test}. Most of the tests passed correctly however some of them have not.

The Functional requirements FR3.4 \& FR4.7 have only been partially fulfilled. This was a purposeful design choice as it would mean that the website would require that Discord servers are added to database and that they would have to be updated when any issues occurred. This was also bad because this list would have to be maintained and could not be automatically updated which would lead to it breaking down the line.